Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2019-04-30 doc/network.tex
stuff

\begin{figure}[ht]
\includegraphics[width=\textwidth]{../fig/cmp_reproductive.pdf}
\caption{\textbf{Comparison of estimates of reproductive number based on various methods.}
Using the observed generation-interval distributions without correcting for right-censoring severely underestimates the reproductive number.
Similarly, using intrinsic and egocentric generation-interval distributions without accounting for local spatial effects overestimates the reproductive number.
Both population-level and individual-level methods provide estimates of reproductive number that are consistent with the empirical estimates, which we define as the average number of secondary cases generated by the first 100 infected individuals.
Boxplots are generated using 100 stochastic simulations of the SEIR model on an empirical network using Ebola-like parameters (see Methods).
}
\label{fig:cmp}
\end{figure}

@@

We classify susceptible depletion into three levels: egocentric, local, and global.
Egocentric susceptible depletion refers to the effect of an infected individual making multiple contacts to the same susceptible individual.
Accounting for the egocentric effect allows us to reinterpret the results by \cite{trapman2016inferring} using arguments based on generation intervals.
Local susceptible depletion refers to the effect of other closely related infected individuals (e.g., in a household or neighborhood) making multiple contacts to the same susceptible individual.
Global susceptible depletion refers to the overall decrease in the susceptible pool in the population.
Egocentric and local depletion effects are important

Limitations
\begin{itemize}
	\item Exponential growth; polynomial
	\item Extending the framework (accounting for control)
	\item Low coverage of gamma
	\item Serial interval
\end{itemize}

\section{Methods}

\subsection{Deterministic SEIR model}

The Susceptible-Exposed-Infected-Recovered (SEIR)

\subsection{Stochastic SEIR model on a network}

>>>>

\begin{figure}[ht]
\includegraphics[width=\textwidth]{../fig/cmp_reproductive.pdf}
\caption{\textbf{Comparison of estimates of reproductive number based on various methods.}
Using the observed generation-interval distributions without correcting for right-censoring severely underestimates the reproductive number.
Similarly, using intrinsic and egocentric generation-interval distributions without accounting for local spatial effects overestimates the reproductive number.
Both population-level and individual-level methods provide estimates of reproductive number that are consistent with the empirical estimates, which we define as the average number of secondary cases generated by the first 100 infected individuals.
Boxplots are generated using 100 stochastic simulations of the SEIR model on an empirical network using Ebola-like parameters.
}
\label{fig:cmp}
\end{figure}

@@

We classify susceptible depletion into three levels: egocentric, local, and global.
Egocentric susceptible depletion refers to the effect of an infected individual making multiple contacts to the same susceptible individual.
Accounting for the egocentric effect allows us to reinterpret the results by \cite{trapman2016inferring} using arguments based on generation intervals.
Local susceptible depletion refers to the effect of other closely related infected individuals (e.g., in a household or neighborhood) making multiple contacts to the same susceptible individual.
Global susceptible depletion refers to the overall decrease in the susceptible pool in the population.
